r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-09-26 r-package/paper2020/paper2020.Rmd
updates paper acknowledgments
additions to paper intro and methods

---
title: 'r5r: Rapid Realistic Routing with R5 in R'
author: "Rafael H. M. Pereira, Marcus Saraiva, Daniel Herszenhut, Carlos Kaue Braga"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  github_document: default
abstract: "write abstract"
urlcolor: blue
vignette: |
  %\VignetteIndexEntry{r5r-intro} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
bibliography: references.json
---

@@

Transport routing is the process of finding the alternative routes and costs 
that connect places on a given transport network. Routing often involves complex
mathematical algorithms and it is a fundamental step required for transport
accessibility analysis, fleet allocation and transport simulation and planning
more broadly. Despite the long-standing importance of routing analysis to the 
field, transport researchers and practitioners still frequently face practical 
challenges with this task. These challenges involve for example the monetary 
costs of licensed software, data availability issues for data hungry models, and
the long computation times to run multiple routing scenarios, particularly in 
large and complex multimodal transport networks. While there is a growing number
of open source routing models [@opentripplanneropentripplanner; 
@lovelace2019stplanr; @padgham2019dodgr], most options available only return the
fastest route option between a set of origins and destinations. This simple
approach overlooks how often people's actual route choices deviate from shortest
travel time paths due to imperfect information, monetary costs and safety issues
among other reasons [@larsen2011travel; @zhu2015people; @conway2019getting].

@@

r5r has low data requirements, enabling routing analysis on different contexts 
wherever there is open data on street networks from OpenStreetMap (OSM). The 
package is also easily scalable allowing for fast computations at either the 
city or country level analysis. For multimodal transport routing, r5r will 
automatically combine OSM data with one or multiple public transport data sets 
in the standard GTFS format to create a routable transport network.

@@

- `travel_time_matrix()`: used to compute travel time estimates between one or 
multiple origin/destination pairs. The origin/destination input can be either a 
spatial `sf POINT` object, or a `data.frame` containing the columns `id`, `lon`, 
`lat.`

- `detailed_itineraries()`:  used to compute detailed information at the trip 
segment level on either the shortest or multiple alternative routes between one
or multiple origin/destination pairs. Includes information such as the transport 
mode, waiting time, travel time and distance.

@@

Conveyal for R5

>>>>

---
title: 'r5r: rapid realistic routing on multimodal transport networks with R5 in R'
author: "Rafael H. M. Pereira, Marcus Saraiva, Daniel Herszenhut, Carlos Kaue Braga"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  github_document: default
abstract: "write abstract"
urlcolor: blue
vignette: |
  %\VignetteIndexEntry{r5r-intro} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
bibliography: references.json
---

@@

Transport routing is the process of finding the alternative routes and costs 
that connect places on a given transport network. Routing often involves complex
mathematical algorithms and it is a fundamental step required for transport
accessibility analysis, fleet allocation and transport simulation and planning
more broadly. Despite the long-standing importance of routing analysis to the 
field of transport and mobility studies, researchers and practitioners still 
frequently face practical challenges with this task. These challenges involve for
example the monetary costs of licensed software, data availability issues for data
hungry models, and the long computation times to run multiple routing scenarios, 
particularly in  large and complex multimodal transport networks.

While there is a growing number of open source routing models [@opentripplanneropentripplanner; 
@lovelace2019stplanr; @padgham2019dodgr], most options available do not efficiently 
process large transport networks. More importantly, these softwares generate
deterministic estimates of travel times without accounting for issues of service
reliability (REF) and they only return the fastest route option  between a set of
origins and destinations. This simple approach overlooks how often people's 
actual route choices deviate from shortest travel time paths, what
can occur due to multiple factors such as imperfect information, monetary costs 
and safety issues [@larsen2011travel; @zhu2015people; @conway2019getting].

@@

r5r has low data requirements, enabling routing analysis on different contexts 
wherever there is open data on street networks from OpenStreetMap (OSM). The 
package is also easily scalable allowing for fast computations at either the 
city or country level analysis. For multimodal transport routing, r5r will 
automatically combine OSM data with one or multiple public transport data sets 
provided by the user in  the standard GTFS format to create a routable transport
network.

@@

- `travel_time_matrix()`: used to compute travel time estimates between one or 
multiple origin/destination pairs for a single departure time or for multiple
departure times over a time window. The origin/destination input can be either a 
spatial `sf POINT` object, or a `data.frame` containing the columns `id`, `lon`, 
`lat.` The output is a `data.frame` with the travel time estimate between each 
origin/destination pair. If the user passes a `time_window` parameter to the,
function, r5r will calculate multiple travel time matrices departing each minute
and return additional information on the percentile distribution of travel times
that allows one to grasp service reliability issues.

- `detailed_itineraries()`: used to compute detailed information on either the
shortest or multiple alternative routes between one or multiple origin/destination
pairs for a single departure time. The output includes detailed information on
route alternatives such as the transport mode, waiting time, travel time and 
distance of each segment of the trip.

@@

The [R<sup>5</sup> routing engine](https://github.com/conveyal/r5) is developed 
at [Conveyal](https://www.conveyal.com/) with contributions from several people. 
This work was supported by the Brazilian Institute for Applied Economic Research 
(Ipea).
